### 2020-04-14 Case Studies/01_geolocation.rmd
geolocation case study
geolocation case study

reshapeSS <- function(data, varSignal = "signal",
                      keepVars = c("posXY", "posX", "posY")) {

   byLocation <- with(data,
                 by(data, list(posXY),
                    function(x) {
                       ans <- x[1, ..keepVars]
                       avgSS <- tapply(x$signal, x$mac, mean)
                       y = matrix(avgSS, nrow = 1, ncol = 6,
                                  dimnames = list(ans$posXY, names(avgSS)))
                       cbind(ans, y)
                    }))

@@

   col_names <- colnames(newDataSS)
   n_cols <- length(col_names)

   colnames(newDataSS)[4:n_cols] <- sapply(col_names[4:n_cols], function(col) {
      n <- nchar(col)
      substr(col, n - 2, n)
   })

   newDataSS[, 4:ncol(newDataSS)] <- round(newDataSS[, 4:ncol(newDataSS)])

@@

>>>>

reshapeSS <- function(data, 
                      varSignal = "signal",
                      keepVars = c("posXY", "posX", "posY"),
                      sampleAngle = F) {

   if(sampleAngle)
      data <- data[angle == sample(data$angle, size = 1), ]

   byLocation <- with(data,
                 by(data, list(posXY),
                    function(x) {
                       ans <- x[1, ..keepVars]
                       avgSS <- tapply(x$signal, x$mac, mean)
                       y = matrix(avgSS, nrow = 1, dimnames = list(ans$posXY, names(avgSS)))
                       cbind(ans, y)
                    }))

@@

   col_names <- colnames(newDataSS)
   to_change <- !(col_names %in% keepVars)

   n_cols <- length(col_names)
   start <- length(keepVars)

   colnames(newDataSS)[to_change] <- sapply(col_names[to_change], function(col) {
      n <- nchar(col)
      substr(col, n - 2, n)
   })

   newDataSS[, start:ncol(newDataSS)] <- round(newDataSS[, start:ncol(newDataSS)])

@@

```{r}
v <- 11;

permuteLocs <- sample(unique(offlineSummary$posXY))
permuteLocs <- matrix(permuteLocs, ncol = v,
                      nrow = floor(length(permuteLocs)/v))

```{r}
onlineFold <- subset(offlineSummary, posXY %in% permuteLocs[, 1])

onlineCVSummary <- reshapeSS(offline, 
                              keepVars = c("posXY", "posX", "posY", "angle"),
                              sampleAngle = T)

onlineFold <- subset(onlineCVSummary,
                     posXY %in% permuteLocs[ , 1])

estFold <- predXY(newSignals = onlineFold[, 6:11],
                  newAngles = onlineFold[, 4],
                  offlineFold, numAngles = 3, k = 3)

actualFold <- onlineFold[, c("posX", "posY")]
calcError(estFold, actualFold)

```{r}
K <- 20
err <- rep(0, K)

for(j in 1:v) {
   onlineFold <- subset(onlineCVSummary,
                        posXY %in% permuteLocs[, j])
   offlineFold <- subset(offlineSummary,
                         posXY %in% permuteLocs[ , -j])

   actualFold <- onlineFold[, c("posX", "posY")]

   for(k in 1:K) {
      estFold <- predXY(newSignals = onlineFold[, 6:11],
                        newAngles = onlineFold[, 4],
                        offlineFold, numAngles = 3, k = k)

      err[k] <- err[k] + calcError(estFold, actualFold) 
   }
}

```{r}
k_values <- data.table(K = 1:K, Error = err, Min = which.min(err))

ggplot(k_values, aes(K, Error)) +
   geom_line(aes(col = Error)) +
   geom_hline(data = k_values[K == Min], aes(yintercept = Error), col = "darkblue") +
   labs("K-NN Training Error")
```

```{r}
estXYk5 <- predXY(newSignals = onlineSummary[, 6:11],
                 newAngles = onlineSummary[, 4],
                 offlineSummary, numAngles = 3, k = 5)
```

```{r}
calcError(estXYk5, actualXY)
```

```{r}
error_table <- data.table(K = c(1, 3, 5), 
                          Error = c(calcError(estXYk1, actualXY), 
                                    calcError(estXYk3, actualXY), 
                                    calcError(estXYk5, actualXY)))

ggplot(error_table, aes(K, Error, fill = -Error)) +
   geom_bar(stat = "identity")
```

```{r}
predXY <- function(newSignals, newAngles, trainData, numAngles = 1, k = 3) {
   chooseXY <- list(length = nrow(newSignals))

   for(i in 1:nrow(newSignals)) {
      trainSS <- selectTrain(newangles[i], trainData, m = numAngles)
      closeXY[[i]] <- findNN(newSignal = as.numeric(newSignals[i, ]),
                             trainSS)
   }

   estXY <- lapply(closeXY, function(x)
                              sapply(x[, 2:3],
                                     function(x) mean(x[1:k])))
   estXY <- do.call("rbind", estXY)

   return(XY)
}

### Follow-up

Write the code to read the raw training data into the data structure in the first approach described in section 1.2. That is, the data structure is a data frame with a column for each MAC address that detected a signal. For the column name, use the last two characters of the MAC address, or some other unique identifier.
